MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2020-03-04 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
fix duplicate code chunk names

### Normalisation - Dx.Tissue.Gender
1. Dx.Tissue.Gender is chosen as the primary variable of interest (i.e., covariate adjustments is conditioned on diagnosis, tissue and reported gender)
2. Individual_ID is chosen as random effect
```{r iterative.normalisation, results='asis'}
COVARIATES$Dx.Tissue.Gender = factor(paste(COVARIATES$Dx.Tissue, COVARIATES$Reported_Gender, sep = "_"))
COVARIATES$Reported_Gender <- NULL
COVARIATES$Dx.Tissue <- NULL
adjust.covars[1] <- "Dx.Tissue.Gender"

@@

### Differential expression analysis (Gender-specific SCZ - Control - Other)
Genes that are differentially expressed at an FDR <= 0.05 are:
```{r set-formula}
formula <- glue::glue("~ 0 + ", glue::glue_collapse(adjust.covars, sep = " + ")) %>% 
  glue::glue(" + (1|{random_effect})")
```

@@

```{r diffExp, fig.height=10, fig.width=15}
L1 = variancePartition::getContrast(exprObj = VOOM.GENE_EXPRESSION, 
                                   formula = formula, 
                                   data = COVARIATES, 
                                   coefficient = c("Dx.Tissue.GenderSCZ_ACC_Female", "Dx.Tissue.GenderControl_ACC_Female"))
L2 = variancePartition::getContrast(exprObj = VOOM.GENE_EXPRESSION, 
                                   formula = formula, 
                                   data = COVARIATES, 
                                   coefficient = c("Dx.Tissue.GenderSCZ_ACC_Male", "Dx.Tissue.GenderControl_ACC_Male"))
L3 = variancePartition::getContrast(exprObj = VOOM.GENE_EXPRESSION, 
                                   formula = formula, 
                                   data = COVARIATES, 
                                   coefficient = c("Dx.Tissue.GenderSCZ_DLPFC_Female", "Dx.Tissue.GenderControl_DLPFC_Female"))
L4 = variancePartition::getContrast(exprObj = VOOM.GENE_EXPRESSION, 
                                   formula = formula, 
                                   data = COVARIATES, 
                                   coefficient = c("Dx.Tissue.GenderSCZ_DLPFC_Male", "Dx.Tissue.GenderControl_DLPFC_Male"))

@@

### Normalisation - Tissue
1. Tissue is chosen as the primary variable of interest (i.e., covariate adjustments is conditioned on diagnosis and reported gender)
2. Individual_ID is chosen as random effect
```{r iterative.normalisation, results='asis'}
###we might not need this adjustment
COVARIATES <- tidyr::separate(COVARIATES, Dx.Tissue.Gender, c("Dx", "Tissue", "Reported_Gender")) %>% 
  dplyr::mutate(Dx = factor(Dx, levels = c("SCZ", "Control", "Other")),
                Tissue = factor(Tissue), 
                Reported_Gender = factor(Reported_Gender))

@@

### Differential expression analysis (ACC - DLPFC)
Genes that are differentially expressed at an FDR <= 0.05 are:
```{r set-formula}
formula <- glue::glue("~ 0 + ", glue::glue_collapse(adjust.covars, sep = " + ")) %>% 
  glue::glue(" + (1|{random_effect})")
```

@@

```{r diffExp, fig.height=10, fig.width=15}
L1 = variancePartition::getContrast(exprObj = VOOM.GENE_EXPRESSION, 
                                   formula = formula, 
                                   data = COVARIATES, 
                                   coefficient = c("TissueDLPFC"))
L2 = variancePartition::getContrast(exprObj = VOOM.GENE_EXPRESSION, 
                                   formula = formula, 
                                   data = COVARIATES, 
                                   coefficient = c("DxSCZ", "DxControl"))
L3 = variancePartition::getContrast(exprObj = VOOM.GENE_EXPRESSION, 
                                   formula = formula, 
                                   data = COVARIATES, 
                                   coefficient = c("Reported_GenderMale"))

>>>>

### Normalisation - Dx.Tissue.Gender
1. Dx.Tissue.Gender is chosen as the primary variable of interest (i.e., covariate adjustments is conditioned on diagnosis, tissue and reported gender)
2. Individual_ID is chosen as random effect
```{r iterative.normalisation-gender, results='asis'}
COVARIATES$Dx.Tissue.Gender = factor(paste(COVARIATES$Dx.Tissue, COVARIATES$Reported_Gender, sep = "_"))
COVARIATES$Reported_Gender <- NULL
COVARIATES$Dx.Tissue <- NULL
adjust.covars[1] <- "Dx.Tissue.Gender"

@@

### Sanity check
```{r residualSigCovars.manual-gender, fig.width=12, fig.height=8}
residualSigCovars[["PC_res"]][[2]]$plotData
```

### Differential expression analysis (Gender-specific SCZ - Control - Other)
Genes that are differentially expressed at an FDR <= 0.05 are:
```{r set-formula-gender}
formula <- glue::glue("~ 0 + ", glue::glue_collapse(adjust.covars, sep = " + ")) %>% 
  glue::glue(" + (1|{random_effect})")
```

@@

```{r diffExp-gender, fig.height=10, fig.width=15}
L1 = variancePartition::getContrast(exprObj = VOOM.GENE_EXPRESSION, 
                                   formula = formula, 
                                   data = COVARIATES, 
                                   coefficient = c("Dx.Tissue.GenderSCZ_ACC_Female", "Dx.Tissue.GenderControl_ACC_Female"))
L2 = variancePartition::getContrast(exprObj = VOOM.GENE_EXPRESSION, 
                                   formula = formula, 
                                   data = COVARIATES, 
                                   coefficient = c("Dx.Tissue.GenderSCZ_ACC_Male", "Dx.Tissue.GenderControl_ACC_Male"))
L3 = variancePartition::getContrast(exprObj = VOOM.GENE_EXPRESSION, 
                                   formula = formula, 
                                   data = COVARIATES, 
                                   coefficient = c("Dx.Tissue.GenderSCZ_DLPFC_Female", "Dx.Tissue.GenderControl_DLPFC_Female"))
L4 = variancePartition::getContrast(exprObj = VOOM.GENE_EXPRESSION, 
                                   formula = formula, 
                                   data = COVARIATES, 
                                   coefficient = c("Dx.Tissue.GenderSCZ_DLPFC_Male", "Dx.Tissue.GenderControl_DLPFC_Male"))

@@

### Normalisation - Tissue
1. Tissue is chosen as the primary variable of interest (i.e., covariate adjustments is conditioned on diagnosis and reported gender)
2. Individual_ID is chosen as random effect
```{r iterative.normalisation-tissue, results='asis'}
###we might not need this adjustment
COVARIATES <- tidyr::separate(COVARIATES, Dx.Tissue.Gender, c("Dx", "Tissue", "Reported_Gender")) %>% 
  dplyr::mutate(Dx = factor(Dx, levels = c("SCZ", "Control", "Other")),
                Tissue = factor(Tissue), 
                Reported_Gender = factor(Reported_Gender))

@@

### Sanity check
```{r residualSigCovars.manual-tissue, fig.width=12, fig.height=8}
residualSigCovars[["PC_res"]][[2]]$plotData
```

### Differential expression analysis (ACC - DLPFC)
Genes that are differentially expressed at an FDR <= 0.05 are:
```{r set-formula-tissue}
formula <- glue::glue("~ 0 + ", glue::glue_collapse(adjust.covars, sep = " + ")) %>% 
  glue::glue(" + (1|{random_effect})")
```

@@

```{r diffExp-tissue, fig.height=10, fig.width=15}
L1 = variancePartition::getContrast(exprObj = VOOM.GENE_EXPRESSION, 
                                   formula = formula, 
                                   data = COVARIATES, 
                                   coefficient = c("TissueDLPFC"))
L2 = variancePartition::getContrast(exprObj = VOOM.GENE_EXPRESSION, 
                                   formula = formula, 
                                   data = COVARIATES, 
                                   coefficient = c("DxSCZ", "DxControl"))
L3 = variancePartition::getContrast(exprObj = VOOM.GENE_EXPRESSION, 
                                   formula = formula, 
                                   data = COVARIATES, 
                                   coefficient = c("Reported_GenderMale"))
